Understanding Broadway Gross: Key Factors and Growth Strategies

### 2024-12-03 paper/paper.qmd
Revise the Result Section
Using modelsummary and modelplot

library(tidyverse)
library(ggplot2)
library(knitr)
library(arrow)
library(here)
library(scales)

@@

This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here] and scales [@scales]. The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets. **ggplot2** is used for data visualization, creating a range of plots to explore and present trends in the data. **knitr** facilitates the integration of analysis and reporting by generating dynamic reports in R Markdown. **arrow** is used for efficient handling of large datasets, particularly for reading and writing data in Parquet format to optimize storage and processing. The **here** package ensures reproducibility by standardizing file paths in the project directory, making it easier to locate and load data files. Finally, **scales** is employed to enhance the readability of plots by formatting axes, labels, and scales, ensuring clarity in the presentation of numeric and categorical data.

@@

# Results {#sec-results}

The results of the multiple linear regression model is summarized in the @tbl-modelresults. The result matches with some of our expectations while deviating in other areas.

As anticipated, average ticket price, seating in theater, and number of performances exhibit significant positive relationships with weekly gross revenue. Specifically, increases in ticket prices and theater size lead to higher gross revenue, consistent with the notion that larger venues and premium ticketing contribute to revenue growth. Similarly, the significant positive impact of the number of performances aligns with our expectation that additional shows increase overall revenue by accommodating more audiences.

@@

However, the results for Tony Award months diverge from our initial expectations. Contrary to the assumption that Tony Award months would boost revenue due to increased demand or publicity, the coefficients for these variables are negative, indicating a slight decrease in weekly gross revenue during these periods.

Lastly, the year variable exhibits a small but positive effect, consistent with the expectation of a gradual upward trend in Broadway revenue over the years. This reflects the broader growth of the industry, potentially due to factors such as inflation. Overall, the model confirms some hypotheses while highlighting discrepancies in the data, prompting further discussion and analysis in the next section.

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: Regression Results for Weekly Gross. This table displays the coefficients, standard errors, and t-statistics for the multiple linear regression model used to analyze the factors influencing weekly gross for Broadway.  
#| warning: false

# Load the regression model
regression_model <- readRDS(here::here("models/regression_model.rds"))
summary <- summary(regression_model)

# Extract the coefficients and form a table with estimates, standard errors, and t-values
coefficients_table <- as.data.frame(summary$coefficients[, 1:3])

# Rename the columns
colnames(coefficients_table) <- c("Coefficient", "Standard Error", "t-Statistic")

# Display the table
kable(coefficients_table, digits = 2)

# Discussion {#sec-discussion}

@@

# Additional Visulization
```{r}
#| label: fig-facet-by-year
#| fig-cap: Average Weekly Gross Revenue Trends Across Months, spanning from 2010 to 2019.
#| echo: false
#| warning: false
#| message: false
# Facet the plot by Year

@@

```
\newpage

>>>>

library(tidyverse)
library(ggplot2)
library(knitr)
library(arrow)
library(here)
library(scales)
library(modelsummary)

@@

This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here], scales [@scales], and modelsummary [@modelsummary]. The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets. **ggplot2** is used for data visualization, creating a range of plots to explore and present trends in the data. **knitr** facilitates the integration of analysis and reporting by generating dynamic reports in R Markdown. **arrow** is used for efficient handling of large datasets, particularly for reading and writing data in Parquet format to optimize storage and processing. The **here** package ensures reproducibility by standardizing file paths in the project directory, making it easier to locate and load data files. Finally, **scales** is employed to enhance the readability of plots by formatting axes, labels, and scales, ensuring clarity in the presentation of numeric and categorical data.

@@

# Results {#sec-results}
The results of the multiple linear regression model are presented in @fig-model, with more detailed information summarized in @tbl-modelresults in [Appendix -@sec-model]. While some findings align with our expectations, others reveal notable deviations.

As anticipated, average ticket price, seating in theater, and number of performances exhibit significant positive relationships with weekly gross revenue. Specifically, increases in ticket prices and theater size lead to higher gross revenue, consistent with the notion that larger venues and premium ticketing contribute to revenue growth. Similarly, the significant positive impact of the number of performances aligns with our expectation that additional shows increase overall revenue by accommodating more audiences. Notably, the confidence intervals for these estimates are relatively narrow, suggesting that the relationships are estimated with high precision and are robust.

@@

The results for Tony Award months diverge from our initial expectations. Contrary to the assumption that Tony Award months would boost revenue due to increased demand or publicity, the coefficients for these variables are negative, suggesting a slight decrease in weekly gross revenue during these periods. Additionally, the confidence interval for this variable is wide and crosses zero, indicating uncertainty about the direction and magnitude of the effect. This suggests that the observed negative coefficient may not represent a consistent trend and warrants caution when interpreting the impact of Tony Award months on revenue.

Lastly, the year variable exhibits a small but positive effect, consistent with the expectation of a gradual upward trend in Broadway revenue over the years. The relatively narrow confidence interval for this variable provides strong support for the observed trend, likely reflecting the broader growth of the industry due to factors such as inflation or expanding audience engagement. Overall, the model confirms some hypotheses while highlighting discrepancies in the data, prompting further discussion and analysis in the next section.

```{r}
#| label: fig-model
#| fig-cap: Coefficient plot illustrating the estimated effects of predictor variables on the response variable. Each point represents the estimated coefficient, and the horizontal lines denote the 95% confidence intervals for each coefficient. Positive values indicate an increasing effect on the response variable, while negative values indicate a decreasing effect.
#| echo: false

# Load the regression model
regression_model <- readRDS(here::here("models/regression_model.rds"))

# Create a custom coefficient name mapping
custom_coef_names <- c(
  "avg_ticket_price" = "Average Ticket Price",
  "seats_in_theatre" = "Seats in Theatre",
  "performances" = "Number of Performances",
  "holiday_week" = "Holiday Week Indicator",
  "Tony_Award" = "Tony Award Winner",
  "year" = "Year"
)

# Extract the data from the modelplot object for labeling
plot_data <- modelplot(
  list("Model Name" = regression_model),
  coef_map = custom_coef_names
)$data

# Ensure the terms are ordered and labeled appropriately
plot_data$term <- factor(plot_data$term, levels = custom_coef_names)

# Generate the coefficient plot with labeled points
coef_plot <- ggplot(plot_data, aes(x = term, y = estimate)) +
  geom_point(size = 2.5) +  # Plot the coefficients as points
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +  # Add confidence intervals
  geom_text(aes(label = round(estimate, 2)), vjust = -1, size = 3) +  # Add coefficient labels
  coord_flip() +  # Flip the axes for better readability
  theme_minimal() +  # Use a clean theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels if needed

# Display the plot
print(coef_plot)
```
# Discussion {#sec-discussion}

@@

\newpage
## Model Summary
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: Regression Results for Weekly Gross. This table displays the coefficients and their confidence intervalsfor the multiple linear regression model used to analyze the factors influencing weekly gross for Broadway.  
#| warning: false

# Load the regression model
regression_model <- readRDS(here::here("models/regression_model.rds"))

# Create a mapping of old names to new names
custom_coef_names <- c(
  "avg_ticket_price" = "Average Ticket Price",
  "seats_in_theatre" = "Seats in Theatre",
  "performances" = "Number of Performances",
  "holiday_week" = "Holiday Week Indicator",
  "Tony_Award" = "Tony Award Winner",
  "year" = "Year"
)

# Generate the summary table with custom coefficient names
output_table <- modelsummary(
  list("Multiple Linear Regression" = regression_model), 
  statistic = "conf.int",
  coef_map = custom_coef_names, # Apply custom coefficient names
  output = "kableExtra"
)

# Display the table
output_table

\newpage
# Additional Visulization

```{r}
#| label: fig-facet-by-year
#| fig-cap: Average Weekly Gross Revenue Trends Across Months, spanning from 2010 to 2019.
#| echo: false
#| warning: false
#| message: false
# Facet the plot by Year

@@
